Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2024-01-06 Manuscript/Manuscript.Rmd
New Figure7

```{r echo=FALSE,fig.cap="**Figure 7. Magnitude of cPRC activation as  a function of stimulus duration and intensity.** Median values of the $AUP$ are presented as a heatmap with dark blue indicating flat $C_P(t)$ traces with median $AUP$ close to 0 and red indicating that the $C_P(t)$ traces have a clearly defined delayed activation peak. "}

knitr::include_graphics(path = "figures/Fig7.svg")
```

>>>>

```{r echo=FALSE,fig.cap="**Figure 7. Comparison of the magnitude of cPRC activation as a function of stimulus duration and intensity.** (**A**) Change in magnitude calculated from mathematical models. Median values of the $AUP$ are presented as a heatmap with dark blue indicating flat $C_P(t)$ traces with median $AUP$ close to 0 and red indicating that the $C_P(t)$ traces have a clearly defined delayed activation peak. (**B**) Change in magnitude calculated from experiments data. The amount of change in cPRC fluorescence intensity (ΔF/F0) when the laser power (%) and time duration (seconds) of the stimulus are varied using calcium imaging. Laser power is shown as relative values. "}

knitr::include_graphics(path = "figures/Fig7.png")
```
